I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-04 Paper/Paper_noProof.tex
Writing

The key point is that, the products of all weights in the paths, have two different signs: along $bc$, the product is (strictly) positive, while along $b'c'$, the product is (strictly) negative.

But if both pairs are negative or positive, LP or even Interval Arithmetic will get the exact values of lower and upper bounds.

The definition of compensating pair is as follows:

@@

	1. A path is a sequence of nodes $\langle a,b,c,d,e,\cdots\rangle$ of nodes from one layer by one layer. We call the first node source node and the last node target node.

@@

	3. A compensating pair is a pair of path with the same starting node and end node, such that the two paths have no common node, and the values of two paths have opposite signs (one is strictly positive and another is strictly negative).

@@

To explain the of meaning of compensating pair, we introduce the following theorems about Diamond:

@@

>>>>

The characteristic is that, the products of all weights in the paths, have two different signs: along $bc$, the product is (strictly) positive, while along $b'c'$, the product is (strictly) negative. This is key reason why fast approximation like LP cannot get the exact upper and lower bounds.

If both pairs are negative or positive, LP or even Interval Arithmetic will get the exact values of lower and upper bounds.

The general formal definition of compensating pair is as follows:

@@

	1. A path is a sequence of nodes $\langle a,b,c,d,e,\cdots\rangle$ of nodes that goes consecutively through each layer. We call the first node source node and the last node target node.

@@

	3. A \emph{compensating pair} is a pair of paths with the same source node and target node, such that the two paths have no common node, and the values of two paths have opposite signs (one is strictly positive and another is strictly negative).

@@

The following theorem shows the meaning of compensating pairs:

@@

In this subsection, we will introduce the method to choose open nodes for MILP model by compensating pairs.
